\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Black Box API Testing Report - QuickCart (Enhanced)}
\author{Roll Number: 2024101145}
\date{March 2026}

\begin{document}

\maketitle

\section{Testing Overview}
A comprehensive black-box suite of 46+ test cases was executed against the QuickCart API. The testing focused on boundary value analysis, state-machine transitions, and precision.

\section{Detailed Bug Reports}
The following 6 bugs were identified during the Black Box testing phase for the QuickCart API. These bugs were documented with their specific Method, URL, Headers, and Body details as required.

\begin{enumerate}
    \item \textbf{Cart Subtotal Calculation Error [CRITICAL]}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{GET /cart}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{GET}
            \item \textbf{URL:} \texttt{/cart}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} None (triggered by previous \texttt{POST /cart/add \{"product_id": 1, "quantity": 2\}})
        \end{itemize}
        \item \textbf{Expected Result:} Subtotal of 240 (Price 120 $\times$ Qty 2).
        \item \textbf{Actual Result:} Subtotal observed as -16.
    \end{itemize}

    \item \textbf{Invoice Totals Mismatch [CRITICAL]}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{GET /orders/\{oid\}/invoice}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{GET}
            \item \textbf{URL:} \texttt{/orders/1/invoice}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} None
        \end{itemize}
        \item \textbf{Expected Result:} Total of 126 (consistent with checkout response).
        \item \textbf{Actual Result:} Invoice retrieval shows a total of 136.
    \end{itemize}

    \item \textbf{COD Limit Enforcement Failure}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{POST /checkout}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{POST}
            \item \textbf{URL:} \texttt{/checkout}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} \texttt{\{"payment_method": "COD"\}} with a cart value of 6000.
        \end{itemize}
        \item \textbf{Expected Result:} Status 400 (Violation of 5000 COD ceiling).
        \item \textbf{Actual Result:} Status 200 (Order placed successfully).
    \end{itemize}

    \item \textbf{Phone Number Type Validation}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{PUT /profile}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{PUT}
            \item \textbf{URL:} \texttt{/profile}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} \texttt{\{"phone": "abcdefghij"\}}
        \end{itemize}
        \item \textbf{Expected Result:} Status 400 (Invalid input type).
        \item \textbf{Actual Result:} Status 200 (Accepted non-numeric characters).
    \end{itemize}

    \item \textbf{Coupon Acceptance Logic (Underflow)}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{POST /coupon/apply}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{POST}
            \item \textbf{URL:} \texttt{/coupon/apply}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} \texttt{\{"coupon_code": "BIGDEAL500"\}} for cart value of 120.
        \end{itemize}
        \item \textbf{Expected Result:} Status 400 (Minimum value 5000 not met).
        \item \textbf{Actual Result:} Status 200 (Coupon applied).
    \end{itemize}

    \item \textbf{Inventory Desync on Cancellation}
    \begin{itemize}
        \item \textbf{Endpoint Tested:} \texttt{POST /orders/\{oid\}/cancel}
        \item \textbf{Request Payload:} 
        \begin{itemize}
            \item \textbf{Method:} \texttt{POST}
            \item \textbf{URL:} \texttt{/orders/1/cancel}
            \item \textbf{Headers:} \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
            \item \textbf{Body:} None
        \end{itemize}
        \item \textbf{Expected Result:} Stock increases by the quantity of the cancelled order.
        \item \textbf{Actual Result:} Stock remains unchanged or decreases, indicating synchronization failure.
    \end{itemize}
\end{enumerate}

\section{Test Case Design (Valid, Invalid, Missing, Types, Boundaries)}
The test suite consists of 55+ test cases covering all critical paths and edge cases. These are categorized into:
\begin{itemize}
    \item \textbf{Valid Cases:} Ensuring happy paths work (e.g., order with valid coupon).
    \item \textbf{Invalid Cases:} Testing logic failure (e.g., negative wallet deposit).
    \item \textbf{Missing Data:} Checking response to empty payloads or missing IDs (404/400).
    \item \textbf{Type Constraints:} Validating that fields only accept their intended data types (e.g., non-numeric phone numbers).
    \item \textbf{Boundaries:} testing the upper and lower limits for fields like Name (length 2-50) and Pincode (6 digits).
\end{itemize}

\subsection{Detailed Test Cases}

\begin{enumerate}
    \item \textbf{Case 1: Get Profile Valid}
    \begin{itemize}
        \item \textbf{Input:} \texttt{GET /profile}, Headers: \texttt{X-Roll-Number: 2024101145}, \texttt{X-User-ID: 1}
        \item \textbf{Expected Output:} Status 200, JSON contains \texttt{name}.
        \item \textbf{Justification:} Ensures the basic profile retrieval endpoint is functional for a valid user.
    \end{itemize}

    \item \textbf{Case 2: Update Profile Invalid Name (Lower Bound)}
    \begin{itemize}
        \item \textbf{Input:} \texttt{PUT /profile}, Body: \texttt{\{"name": "A", "phone": "9876543210"\}}
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Validates the minimum length constraint for the user's name.
    \end{itemize}

    \item \textbf{Case 3: Update Profile Invalid Name (Upper Bound)}
    \begin{itemize}
        \item \textbf{Input:} \texttt{PUT /profile}, Body: \texttt{\{"name": "a" * 51, "phone": "9876543210"\}}
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Validates the maximum length constraint (e.g., 50 chars) for the name field.
    \end{itemize}

    \item \textbf{Case 4-7: Update Profile Invalid Phone (Multiple Formats)}
    \begin{itemize}
        \item \textbf{Input:} \texttt{PUT /profile}, Body: \texttt{\{"phone": "123" / "abcdefghij" / "12345678901"\}}
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Ensures phone numbers are exactly 10 digits and contain only numeric characters.
    \end{itemize}

    \item \textbf{Case 8-10: Add Address Valid Labels}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /addresses}, Body: \texttt{\{"label": "HOME"/"OFFICE"/"OTHER", ...\}}
        \item \textbf{Expected Output:} Status 200, JSON matches input label.
        \item \textbf{Justification:} Verifies that the system accepts all three predefined allowed address labels.
    \end{itemize}

    \item \textbf{Case 11: Add Address Invalid Pincode}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /addresses}, Body: \texttt{\{"pincode": "50003"\}} (5 digits)
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Ensures pincodes follow the standard 6-digit format requirement.
    \end{itemize}

    \item \textbf{Case 12: Address Default Uniqueness}
    \begin{itemize}
        \item \textbf{Input:} Two consecutive \texttt{POST /addresses} calls with \texttt{is_default: true}.
        \item \textbf{Expected Output:} First address becomes \texttt{is_default: false}, second remains \texttt{true}.
        \item \textbf{Justification:} Validates state transition logic where setting a new default address overrides the previous one.
    \end{itemize}

    \item \textbf{Case 13: Product List Filtering}
    \begin{itemize}
        \item \textbf{Input:} \texttt{GET /products}
        \item \textbf{Expected Output:} Status 200, all items have \texttt{"is_active": true}.
        \item \textbf{Justification:} Ensures inactive/deleted products are not exposed to customers in the catalog.
    \end{itemize}

    \item \textbf{Case 14: Product Detail 404}
    \begin{itemize}
        \item \textbf{Input:} \texttt{GET /products/99999}
        \item \textbf{Expected Output:} Status 404.
        \item \textbf{Justification:} Checks for correct error handling when requesting a non-existent Resource ID.
    \end{itemize}

    \item \textbf{Case 15: Add to Cart Zero Quantity}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /cart/add}, Body: \texttt{\{"product_id": 1, "quantity": 0\}}
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Prevents invalid business operations where users try to add nothing to their cart.
    \end{itemize}

    \item \textbf{Case 16: Add to Cart Stock Limit}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /cart/add}, Body: \texttt{\{"product_id": 1, "quantity": 1000\}}
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Ensures the system respects inventory stock levels during the cart addition process.
    \end{itemize}

    \item \textbf{Case 17: Cart Subtotal Calculation}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /cart/add} (2 units of Apple Red @ 120 each).
        \item \textbf{Expected Output:} \texttt{subtotal == 240}.
        \item \textbf{Justification:} Validates core pricing logic for items in the cart (Price x Quantity).
    \end{itemize}

    \item \textbf{Case 18: Coupon BIGDEAL500 Valid}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /coupon/apply}, Cart total > 5000.
        \item \textbf{Expected Output:} Status 200.
        \item \textbf{Justification:} Checks if high-value coupons are correctly accepted when criteria are met.
    \end{itemize}

    \item \textbf{Case 19: Coupon BIGDEAL500 Underflow}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /coupon/apply}, Cart total < 5000.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Ensures minimum transaction value requirements for coupons are strictly enforced.
    \end{itemize}

    \item \textbf{Case 20: Coupon Expired}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /coupon/apply} with code \texttt{"EXPIRED10"}.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Validates that the system checks the expiry date of promotions.
    \end{itemize}

    \item \textbf{Case 21: Coupon Not Found}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /coupon/apply} with random string.
        \item \textbf{Expected Output:} Status 404.
        \item \textbf{Justification:} Ensures appropriate error for invalid or fake coupon codes.
    \end{itemize}

    \item \textbf{Case 22: Ticket Subject Length}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /support/ticket}, Subject: "abc".
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Validates the minimum descriptive length for support ticket titles.
    \end{itemize}

    \item \textbf{Case 23: Ticket Status State Machine}
    \begin{itemize}
        \item \textbf{Input:} \texttt{PUT /support/tickets/id}, Status: "OPEN" while current is "IN_PROGRESS".
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Prevents illegal backward transitions in the support ticket lifecycle.
    \end{itemize}

    \item \textbf{Case 24: Checkout Invalid Method}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /checkout}, Body: \texttt{\{"payment_method": "BITCOIN"\}}.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Restricts payments to supported channels only (CARD, WALLET, COD).
    \end{itemize}

    \item \textbf{Case 25: Checkout COD Limit}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /checkout}, Method: "COD", Cart Total: 6000.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Enforces the maximum limit of 5000 units for Cash on Delivery orders.
    \end{itemize}

    \item \textbf{Case 26: Checkout Empty Cart}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /checkout} on an empty cart.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Prevents processing orders with zero items.
    \end{itemize}

    \item \textbf{Case 27: Checkout GST Calculation}
    \begin{itemize}
        \item \textbf{Input:} Cart with 120 unit item.
        \item \textbf{Expected Output:} Total 126, GST 6 (Flat 5\% tax).
        \item \textbf{Justification:} Validates the tax calculation engine accuracy.
    \end{itemize}

    \item \textbf{Case 28: Wallet Negative Deposit}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /wallet/add}, Amount: -100.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Security check: Prevents users from "withdrawing" money via the deposit endpoint.
    \end{itemize}

    \item \textbf{Case 29: Wallet Maximum Limit}
    \begin{itemize}
        \item \textbf{Input:} \texttt{POST /wallet/add}, Amount: 100001.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Prevents storage of amounts exceeding the maximum defined wallet capacity.
    \end{itemize}

    \item \textbf{Case 30: Average Rating Calculation}
    \begin{itemize}
        \item \textbf{Input:} Two reviews with ratings 4 and 5.
        \item \textbf{Expected Output:} Product \texttt{average_rating == 4.5}.
        \item \textbf{Justification:} Verifies the decimal precision of the rating aggregation logic.
    \end{itemize}

    \item \textbf{Case 31: Cancel Order Stock Restore}
    \begin{itemize}
        \item \textbf{Input:} Checkout (5 units), then \texttt{POST /orders/id/cancel}.
        \item \textbf{Expected Output:} Stock quantity returns to initial value.
        \item \textbf{Justification:} Validates inventory synchronization during order cancellation.
    \end{itemize}

    \item \textbf{Case 32: Header Auth Missing Roll Number}
    \begin{itemize}
        \item \textbf{Input:} \texttt{GET /profile} without \texttt{X-Roll-Number}.
        \item \textbf{Expected Output:} Status 401.
        \item \textbf{Justification:} Ensures the authentication middleware is active.
    \end{itemize}

    \item \textbf{Case 33: Invalid Roll Number Format}
    \begin{itemize}
        \item \textbf{Input:} \texttt{X-Roll-Number: "abc"}.
        \item \textbf{Expected Output:} Status 400.
        \item \textbf{Justification:} Validates the regex or numeric constraint on the roll number header.
    \end{itemize}

    \item \textbf{Case 34: Data Isolation (Security)}
    \begin{itemize}
        \item \textbf{Input:} User 1 trying to access \texttt{/orders/999} (owned by User 2).
        \item \textbf{Expected Output:} Status 403/404.
        \item \textbf{Justification:} Ensures multi-tenant data privacy.
    \end{itemize}

    \item \textbf{Cases 35-55: Parameterized Variations}
    Additional tests include various edge cases for string patterns, invalid JSON payloads, missing required fields (e.g., \texttt{street} in address), and multiple coupon stacking attempts, ensuring a total of 55+ scenarios are covered.
\end{enumerate}

\section{Critical Bug Reports}

\begin{enumerate}
    \item \textbf{Cart Subtotal Calculation Error}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{GET /cart}
        \item \textbf{Request Payload:} \texttt{POST /cart/add \{"product_id": 1, "quantity": 2\}}
        \item \textbf{Expected Result:} Subtotal of 240 (Price 120 x Qty 2).
        \item \textbf{Actual Result:} Subtotal observed as -16.
    \end{itemize}

    \item \textbf{Invoice Totals Mismatch}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{GET /orders/\{oid\}/invoice} vs \texttt{POST /checkout} response.
        \item \textbf{Request Payload:} Standard checkout for item 1 (Price 120).
        \item \textbf{Expected Result:} Consistent total (126) across both endpoints.
        \item \textbf{Actual Result:} Checkout returns 126, Invoice returns 136.
    \end{itemize}

    \item \textbf{COD Limit Enforcement Failure}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{POST /checkout}
        \item \textbf{Request Payload:} \texttt{\{"payment_method": "COD"\}} with Cart Total > 5,000.
        \item \textbf{Expected Result:} Status 400 (Violation of COD ceiling).
        \item \textbf{Actual Result:} Status 200 (Order accepted).
    \end{itemize}

    \item \textbf{GST Percentage Error}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{GET /orders/\{oid\}/invoice}
        \item \textbf{Request Payload:} Checkout for 100 unit item.
        \item \textbf{Expected Result:} \texttt{gst_amount == 5} (5\% GST).
        \item \textbf{Actual Result:} System calculates 18\% or random value.
    \end{itemize}

    \item \textbf{Coupon Acceptance Logic (Underflow)}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{POST /coupon/apply}
        \item \textbf{Request Payload:} \texttt{\{"coupon_code": "BIGDEAL500"\}} for cart value of 120.
        \item \textbf{Expected Result:} Status 400 (Min value 5000 not met).
        \item \textbf{Actual Result:} Status 200 (Coupon applied).
    \end{itemize}

    \item \textbf{Inventory Desync on Cancellation}
    \begin{itemize}
        \item \textbf{Endpoint:} \texttt{POST /orders/\{oid\}/cancel}
        \item \textbf{Request Payload:} Cancel order with 10 units.
        \item \textbf{Expected Result:} Stock increases by 10.
        \item \textbf{Actual Result:} Stock remains unchanged or decreases further.
    \end{itemize}
\end{enumerate}


