\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Integration Testing Report - StreetRace Manager}
\author{Roll Number: 2024101145}
\date{March 2026}

\begin{document}

\maketitle

\section{Call Graph}
The system's integration Call Graphs were hand-drawn and are stored in the \texttt{integration/diagrams/} directory. These graphs illustrate the flow of control and data between modules such as \texttt{Registration}, \texttt{Inventory}, and the extra modules.

\section{Module Descriptions}
The system consists of the following core modules located in the \texttt{racing/} directory. Note: The code module has been renamed to \texttt{racing} to avoid common namespace conflicts during testing.
\begin{itemize}
    \item \textbf{Registration:} Handles crew onboarding and member verification.
    \item \textbf{Crew Management:} Assigns driver/mechanic roles to members.
    \item \textbf{Inventory:} Tracks cars, cash, fuel, and vehicle damage state.
    \item \textbf{Race Management:} Handles race creation, participant logic, and entry checks.
    \item \textbf{Results:} Processes rankings, calculates prize money, and updates financial state.
    \item \textbf{Mission Planning:} Handles role-based heist/mission assignments and resource checks.
\end{itemize}

\section{Extra Modules}
\begin{enumerate}
    \item \textbf{Betting Module:} Integrates with \texttt{Inventory} to allow wagering on race results. It deducts stakes and credits winners based on results fetched from \texttt{RaceManagement}.
    \item \textbf{Reputation Module:} Integrates with \texttt{Registration} to track cumulative experience/rep points across multiple races and missions.
\end{enumerate}

\section{Integration Finding Summary}
An integration test suite consisting of 10 test cases following the required format was developed to verify the StreetRace Manager's component interaction.

The findings indicate that the multi-module interactions across different components work correctly. For example:
\begin{enumerate}
    \item \textbf{Mission Assignment:} The \texttt{MissionPlanningModule} correctly verifies crew members and their roles.
    \item \textbf{Race Prize Money:} The \texttt{ResultsModule} correctly processes race rankings and awards prize money, with the \texttt{InventoryModule} showing appropriate balance updates.
\end{enumerate}

\section{Integration Test Cases}
The integration suite contains 10+ interaction scenarios designed to verify data consistency across the StreetRace modules.

\begin{enumerate}
    \item \textbf{Full Race Lifecycle}
    \begin{itemize}
        \item \textbf{Components:} Registration, Inventory, Race Management, Results.
        \item \textbf{Input/Flow:} Register "Dom", buy "Charger" (2000), win race (1000 prize).
        \item \textbf{Outcome:} Cash balance = 4000 (5000 - 2000 + 1000).
        \item \textbf{Justification:} Verifies the end-to-end race flow and financial ledger consistency across 4 modules.
    \end{itemize}

    \item \textbf{Mission Safety Check (Mechanic Role)}
    \begin{itemize}
        \item \textbf{Components:} Registration, Inventory, Mission Planning.
        \item \textbf{Input/Flow:} Damage "Supra", attempt mission without a mechanic.
        \item \textbf{Outcome:} Mission failure (\texttt{success == False}).
        \item \textbf{Justification:} Ensures the Mission module queries the Registration module for necessary human capital skills.
    \end{itemize}

    \item \textbf{Role-Based Race Restriction}
    \begin{itemize}
        \item \textbf{Components:} Registration, Race Management.
        \item \textbf{Input/Flow:} Register "Mia" as strategist, attempt to race.
        \item \textbf{Outcome:} \texttt{success == False} (Invalid role error).
        \item \textbf{Justification:} Validates that business rules in the Race module are correctly enforced via the Registration service.
    \end{itemize}

    \item \textbf{Financial Guardrail Integration}
    \begin{itemize}
        \item \textbf{Components:} Inventory.
        \item \textbf{Input/Flow:} Try to buy "ExpensiveCar" (10000) with 5000 budget.
        \item \textbf{Outcome:} \texttt{success == False} (Insufficient funds).
        \item \textbf{Justification:} Ensures the Inventory module self-regulates its internal state during large transactions.
    \end{itemize}

    \item \textbf{Registration Deduplication}
    \begin{itemize}
        \item \textbf{Components:} Registration.
        \item \textbf{Input/Flow:} Register the same name twice.
        \item \textbf{Outcome:} \texttt{success == False} (Already registered).
        \item \textbf{Justification:} Ensures data integrity and prevents ID collisions in the onboarding module.
    \end{itemize}

    \item \textbf{Inventory Asset Destruction}
    \begin{itemize}
        \item \textbf{Components:} Inventory, Mission Planning.
        \item \textbf{Input/Flow:} Delete a car from the inventory, then try to assign it to a mission.
        \item \textbf{Outcome:} \texttt{success == False} (Car not found in inventory).
        \item \textbf{Justification:} Validates that Mission Planning relies on real-time Inventory status.
    \end{itemize}

    \item \textbf{Mission Profit Synchronization}
    \begin{itemize}
        \item \textbf{Components:} Mission Planning, Results, Inventory.
        \item \textbf{Input/Flow:} Complete heist mission and record 5000 profit.
        \item \textbf{Outcome:} Total cash balance increases to 10000.
        \item \textbf{Justification:} Verifies that high-stakes payouts are correctly funneled back into the primary ledger.
    \end{itemize}

    \item \textbf{Crew Management Scalability}
    \begin{itemize}
        \item \textbf{Components:} Registration, Crew Management.
        \item \textbf{Input/Flow:} Bulk register 10 drivers.
        \item \textbf{Outcome:} Crew manager returns 10 available members.
        \item \textbf{Justification:} Ensures the cross-registration bridge between modules doesn't scale poorly or lose records.
    \end{itemize}

    \item \textbf{Multi-Role Crew Requirement}
    \begin{itemize}
        \item \textbf{Components:} Mission Planning, Registration.
        \item \textbf{Input/Flow:} Mission requiring both a driver and a mechanic for a damaged car.
        \item \textbf{Outcome:} Mission failure if only drivers are assigned.
        \item \textbf{Justification:} Checks boolean logic for complex multi-participant resource checks.
    \end{itemize}

    \item \textbf{Future Transaction Bridge}
    \begin{itemize}
        \item \textbf{Components:} Results, Inventory.
        \item \textbf{Input/Flow:} Use prize money from Race 1 to buy a high-value car in a future step.
        \item \textbf{Outcome:} Transaction succeeds only after a previous win.
        \item \textbf{Justification:} Validates chronological state progression across different module interactions.
    \end{itemize}
\end{enumerate}

\end{document}
