\documentclass{article}
\usepackage[utf8]{inputenc}

\title{White Box Testing Report - MoneyPoly}
\author{Roll Number: 2024101145}
\date{March 2026}

\begin{document}

\maketitle

\section{Control Flow Graph (CFG)}
The Control Flow Graphs for the core game logic (Bank loan, Player net worth, Property rent doubling) were hand-drawn and are attached in the \texttt{whitebox/diagrams/} directory as required by the assignment guidelines.

\section{Code Quality Analysis}
The codebase was analyzed using \texttt{pylint}. Iterative changes were made to address warnings:
\begin{itemize}
    \item Fixed missing module and class docstrings.
    \item Simplified complex branching in \texttt{game.py}.
    \item Reduced redundant variable assignments and improved naming conventions.
    \item Fixed the bank loan fund leakage bug and player net worth calculation.
\end{itemize}

\section{White Box Test Cases and Logical Isssues}
Designed white-box test cases for the MoneyPoly game structure, covering all branches, key variable states, and edge cases.

\begin{enumerate}
    \item \textbf{Test Case: Player Standard Movement}
    \begin{itemize}
        \item \textbf{Why needed:} Validates the basic state update of the \texttt{position} variable.
        \item \textbf{Logic/Errors Found:} Initially, movement was strictly positional and did not account for modular board wrap-around logic in all edge cases.
    \end{itemize}

    \item \textbf{Test Case: Board Wrap-Around (Pass Go Salary)}
    \begin{itemize}
        \item \textbf{Why needed:} Tests the boundary condition where \texttt{position} exceeds \texttt{BOARD_SIZE}.
        \item \textbf{Logic/Errors Found:} \textbf{Major Logical Issue:} The code originally only awarded salary if the player landed \textit{exactly} on position 0. It failed to award salary when \textit{passing} Go during a large move. Corrected to check if \texttt{new_position < old_position}.
    \end{itemize}

    \item \textbf{Test Case: Player Net Worth Calculation}
    \begin{itemize}
        \item \textbf{Why needed:} Verifies that the net worth variable accurately reflects both liquid cash and asset value.
        \item \textbf{Logic/Errors Found:} \textbf{Error Found:} The function returned only \texttt{self.balance}. It missed the sum of \texttt{prop.price} for all owned properties. Fixed by iterating through \texttt{self.properties}.
    \end{itemize}

    \item \textbf{Test Case: Bank Loan Fund Integrity}
    \begin{itemize}
        \item \textbf{Why needed:} Ensures the Bank's internal \texttt{_funds} variable is synchronized with payouts.
        \item \textbf{Logic/Errors Found:} \textbf{Critical Issue:} The \texttt{give_loan} method added money to the player but did not deduct it from the bank's reserves, creating "phantom money". Fixed to call \texttt{pay_out}.
    \end{itemize}

    \item \textbf{Test Case: Dice Roll Range (1-6)}
    \begin{itemize}
        \item \textbf{Why needed:} Validates the stochastic boundary of the dice component.
        \item \textbf{Logic/Errors Found:} \textbf{Bug Found:} Used \texttt{random.randint(1, 5)}, making it impossible to roll a 6 or certain doubles combinations. Fixed to \texttt{(1, 6)}.
    \end{itemize}

    \item \textbf{Test Case: Triple Doubles (Jail Logic)}
    \begin{itemize}
        \item \textbf{Why needed:} Tests the state transition based on the \texttt{doubles_streak} counter.
        \item \textbf{Logic/Errors Found:} \textbf{Bug Found:} The \texttt{Dice} class was missing the \texttt{is_triple_doubles()} method, leading to an \texttt{AttributeError} when the condition was met. Added the method.
    \end{itemize}

    \item \textbf{Test Case: Rent Doubling (Full Group Ownership)}
    \begin{itemize}
        \item \textbf{Why needed:} Tests complex branch logic in the \texttt{get_rent()} method.
        \item \textbf{Logic/Errors Found:} Verified that the multiplier is only applied when every property in the \texttt{PropertyGroup} is owned by the same player.
    \end{itemize}

    \item \textbf{Test Case: Mortgage State Transitions}
    \begin{itemize}
        \item \textbf{Why needed:} Tests the \texttt{is_mortgaged} flag and its effect on rent and availability.
        \item \textbf{Logic/Errors Found:} Ensures rent returns 0 when mortgaged, preventing illegal income.
    \end{itemize}

    \item \textbf{Test Case: Bank Insufficient Funds Payout}
    \begin{itemize}
        \item \textbf{Why needed:} Edge case for when the bank's capital pool is exhausted.
        \item \textbf{Logic/Errors Found:} Validated that a \texttt{ValueError} is raised with a clear message, preventing negative bank balances.
    \end{itemize}

    \item \textbf{Test Case: Player Negative Deduction/Addition}
    \begin{itemize}
        \item \textbf{Why needed:} Edge case for unexpected input values (negative amounts).
        \item \textbf{Logic/Errors Found:} Added guard clauses and \texttt{ValueError} raises for negative inputs to prevent accounting corruption.
    \end{itemize}
\end{enumerate}

\section{Detailed Bug Reports}
As required, the following errors were corrected, and each change was saved as a specific "Error #" commit.

\begin{enumerate}
    \item \textbf{Error 1: Move logic and Salary}
    \begin{itemize}
        \item \textbf{Issue:} Passing Go did not award \$200.
        \item \textbf{Fix:} Updated \texttt{Player.move()} to check \texttt{new_pos < old_pos}.
    \end{itemize}
    \item \textbf{Error 2: Dice Range}
    \begin{itemize}
        \item \textbf{Issue:} \texttt{randint(1, 5)} excluded 6.
        \item \textbf{Fix:} Updated to \texttt{randint(1, 6)} in \texttt{dice.py}.
    \end{itemize}
    \item \textbf{Error 3: Missing Jail Method}
    \begin{itemize}
        \item \textbf{Issue:} \texttt{is_triple_doubles()} was undefined.
        \item \textbf{Fix:} Added method to \texttt{Dice} class.
    \end{itemize}
\end{enumerate}
\end{document}
