\documentclass{article}
\usepackage[utf8]{inputenc}

\title{White Box Testing Report - MoneyPoly}
\author{Roll Number: 2024101145}
\date{March 2026}

\begin{document}

\maketitle

\section{Control Flow Graph (CFG)}
The Control Flow Graphs for the core game logic (Bank loan, Player net worth, Property rent doubling) were hand-drawn and are attached in the \texttt{whitebox/diagrams/} directory as required by the assignment guidelines.

\section{Code Quality Analysis}
The codebase was analyzed using \texttt{pylint}. Iterative changes were made to address warnings:
\begin{itemize}
    \item Fixed missing module and class docstrings.
    \item Simplified complex branching in \texttt{game.py}.
    \item Reduced redundant variable assignments and improved naming conventions.
    \item Fixed the bank loan fund leakage bug and player net worth calculation.
\end{itemize}

\section{Bugs Found and Fixed}
A white-box test suite consisting of 50+ test cases was developed and executed for the MoneyPoly game engine. The suite covers core components including the Bank, Player, Board, and Property management systems.

\begin{enumerate}
    \item \textbf{Bank Loan Fund Integrity [CRITICAL]:} 
    When a player takes a loan, the bank funds are not correctly deducted in the original code. The player receives the cash, but the bank's internal balance remains unchanged, allowing for infinite money creation. This was fixed by calling \texttt{self.pay_out(payout_amount)} within the \texttt{give_loan} method.
    \item \textbf{Player Net Worth Calculation Error:} 
    The \texttt{get_net_worth()} function in the \texttt{Player} class originally only considered liquid cash. It failed to account for the value of properties owned by the player. This was corrected by adding a loop to iterate through the player's property list and summing their market values.
\end{enumerate}

\section{White Box Test Cases}
The test suite consists of 50+ collector items and cases, meticulously designed to validate the internal logic of the MoneyPoly game engine.

\subsection{Bank Operations (20+ Cases)}
\begin{enumerate}
    \item \textbf{Initial Fund Verification}
    \begin{itemize}
        \item \textbf{Input:} \texttt{Bank()} instance.
        \item \textbf{Expected Output:} Initial balance > 0, 0 loans.
        \item \textbf{Justification:} Ensures the bank object initializes with a standard capital pool.
    \end{itemize}

    \item \textbf{Fund Collection}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.collect(100)}.
        \item \textbf{Expected Output:} Internal balance increases by exactly 100.
        \item \textbf{Justification:} Validates deposit logic (income from taxes/properties).
    \end{itemize}

    \item \textbf{Payout Logic}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.pay_out(500)}.
        \item \textbf{Expected Output:} Returns 500, balance decreases by 500.
        \item \textbf{Justification:} Ensures money is correctly withdrawn from the reserve for payouts.
    \end{itemize}

    \item \textbf{Insufficient Funds Payout}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.pay_out(bank.get_balance() + 1)}.
        \item \textbf{Expected Output:} \texttt{ValueError} with diagnostic message.
        \item \textbf{Justification:} Prevents the bank from going into an illegal negative state.
    \end{itemize}

    \item \textbf{Loan Issuance State Change}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.give_loan(player1, 1000)}.
        \item \textbf{Expected Output:} Player balance inc 1000, loan\_count inc 1.
        \item \textbf{Justification:} Validates the multi-state update during the loan process.
    \end{itemize}

    \item \textbf{Zero-Value Loan Handling}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.give_loan(player, 0)}.
        \item \textbf{Expected Output:} No change in loan count.
        \item \textbf{Justification:} Gracefully ignores non-operational loan requests.
    \end{itemize}
\end{enumerate}

\subsection{Player Logic (20+ Cases)}
\begin{enumerate}
    \item \textbf{Standard Movement}
    \begin{itemize}
        \item \textbf{Input:} \texttt{player.move(5)}.
        \item \textbf{Expected Output:} \texttt{position == 5}.
        \item \textbf{Justification:} Validates basic position updates.
    \end{itemize}

    \item \textbf{Board Wrap-Around (GO Pass)}
    \begin{itemize}
        \item \textbf{Input:} \texttt{player.move(36)} from pos 5 (Total 41).
        \item \textbf{Expected Output:} \texttt{position == 1}, \texttt{balance += 200}.
        \item \textbf{Justification:} Ensures salary is credited and modulo arithmetic is correct for the 40-tile board.
    \end{itemize}

    \item \textbf{Net Worth (Liquid Cash)}
    \begin{itemize}
        \item \textbf{Input:} \texttt{player.balance = 1000}.
        \item \textbf{Expected Output:} \texttt{net_worth() == 1000}.
        \item \textbf{Justification:} Basic net worth check.
    \end{itemize}

    \item \textbf{Jail Transition}
    \begin{itemize}
        \item \textbf{Input:} \texttt{player.go_to_jail()}.
        \item \textbf{Expected Output:} \texttt{in_jail == True}, \texttt{position == 10}.
        \item \textbf{Justification:} Ensures state and position are synchronized during penalties.
    \end{itemize}

    \item \textbf{Negative Fund Management}
    \begin{itemize}
        \item \textbf{Input:} \texttt{player.add_money(-1)}.
        \item \textbf{Expected Output:} \texttt{ValueError}.
        \item \textbf{Justification:} Prevents logical errors in the accounting module.
    \end{itemize}
\end{enumerate}

\subsection{Property and Management (10+ Cases)}
\begin{enumerate}
    \item \textbf{Rent Doubling Rule}
    \begin{itemize}
        \item \textbf{Input:} Ownership of full color group (e.g., P1 and P2).
        \item \textbf{Expected Output:} \texttt{p1.get_rent()} returns $2 \times$ base rent.
        \item \textbf{Justification:} Validates board economics and group ownership logic.
    \end{itemize}

    \item \textbf{Mortgage Mechanism}
    \begin{itemize}
        \item \textbf{Input:} \texttt{property.mortgage()}.
        \item \textbf{Expected Output:} \texttt{is_mortgaged == True}, \texttt{rent == 0}, \texttt{player_balance += 50}.
        \item \textbf{Justification:} Checks state transitions for mortgaged properties.
    \end{itemize}

    \item \textbf{Unmortgage Cost Calculation}
    \begin{itemize}
        \item \textbf{Input:} \texttt{property.unmortgage()} for a 50 loan.
        \item \textbf{Expected Output:} \texttt{cost == 55} (10\% processing fee).
        \item \textbf{Justification:} Validates the interest rate logic for lifting mortgages.
    \end{itemize}
\end{enumerate}

\section{Detailed Bug Reports}

\begin{enumerate}
    \item \textbf{Bank Loan Fund Leak [CRITICAL]}
    \begin{itemize}
        \item \textbf{Input:} \texttt{bank.give_loan(player, 1000)} where Bank balance = 50,000.
        \item \textbf{Expected Result:} \texttt{bank_balance == 49,000}.
        \item \textbf{Actual Result:} \texttt{bank_balance == 50,000}.
        \item \textbf{Root Cause:} The \texttt{give_loan} method adds money to the player's wallet but forgets to call the internal \texttt{pay_out} or deduction method for the bank's own reserves.
    \end{itemize}

    \item \textbf{Player Net Worth Value Error}
    \begin{itemize}
        \item \textbf{Input:} Player with \$500 cash and owning "Park Place" (Value: \$350).
        \item \textbf{Expected Result:} \texttt{net_worth() == 850}.
        \item \textbf{Actual Result:} \texttt{net_worth() == 500}.
        \item \textbf{Root Cause:} The \texttt{get_net_worth()} implementation only sums the \texttt{self.balance} attribute and does not iterate through the \texttt{self.properties} list to add their current market value.
    \end{itemize}
\end{enumerate}

\end{document}
